\section{Meeting Abstracts}

\begin{etaremune}
\item \YZhang, Byrnes, J. S., \SWei, \Me, \FWang, \& Bezada M. (2021).
    P-wave attenuation tomography of the Tonga-Lau mantle wedge improved
    by a Bayesian Monte Carlo approach and independently constrained source spectra.
    Abstract S25D-0276 virtually presented at 2021 AGU Fall Meeting.
\item Meghan, J., Grund, M., Schlitzer, W., Leong, W. J., \Me, \JYao, \& \LUieda\ (2021).
    PyGMT: An open-source Python library for geospatial processing, analysis, and visualization.
    Abstract IN55C-08 virtually presented at 2021 AGU Fall Meeting.
\item \SWei, \YZhang, \Me, \& \DWiens\ (2021).
    New advances in body-wave attenuation studies of the Tonga subduction zone.
    Abstract S23B-05 virtually presented at 2021 AGU Fall Meeting.
\item \Me, \& \SWei\ (2021).
    Source spectra and stress drops of small-to-moderate earthquakes beneath the Alaska peninsula.
    Abstract T54A-11 virtually presented at 2021 AGU Fall Meeting.
\item \SWei, \PShearer, \CLithgowBertelloni, \LStixrude, \& \Me\ (2021).
    Oceanic plateau of the Hawaiian mantle plume head subducted to the uppermost lower mantle.
    Abstract EGU21-13874 virtually presented at EGU General Assembly 2021.
\item \Me, \WWang, \FWang, \& \SWei\ (2020).
    Source spectra of intermediate-depth and deep earthquakes in the Tonga subduction zone.
    Abstract S054-0012 virtually presented at 2020 AGU Fall Meeting.
\item \SWei, \Me, \PShearer, \MLv, \SDorfman, \CLithgowBertelloni, \& \LStixrude\ (2020).
    Compositional heterogeneities in the mid-mantle revealed by seismic discontinuities and reflectors.
    Abstract DI016-0008 virtuablly presented at 2020 AGU Fall Meeting.
\item \Me, \WWang, \& \SWei\ (2019).
    Source spectra and stress drop of deep earthquakes in the Tonga subduction zone.
    Abstract S13C-0458 presented at 2019 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Me, \SWei, \& \PShearer\ (2019).
    Global variations of the 520-km discontinuity.
    Presented at Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Me, \SWei, \& \PShearer\ (2018).
    Global variations of the 520-km discontinuity.
    Abstract DI31C-0024 presented at 2018 AGU Fall Meeting, Washington, DC, USA.
\item
    \Me, \JYao, \& \LWen\ (2017).
    Collapse and earthquake swarm after North Korea's 3 September 2017 nuclear test.
    Abstract S43H-2968 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    \Me, \& \LWen\ (2017).
    Three types of Earth's inner core boundary.
    Abstract DI33B-0404 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    \JYao, \Me, \& \LWen\ (2017).
    High-precision location, yield and tectonic release of North Korea's 3 September 2017 nuclear test.
    Abstract S43H-2967 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    \JYao, \Me, \LSun, \& \LWen\ (2017).
    Temporal change of seismic Earth's inner core phases: Inner core differential rotation or temporal change of inner core surface?
    Abstract DI33B-0405 presented at 2017 AGU Fall Meeting, New Orleans, LA, USA.
\item
    \Me, \& \LWen\ (2017).
    Seismological evidence for a localized mushy zone at the Earth's inner core boundary.
    Presented at Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \JYao, \Me, \LSun, \& \LWen\ (2017).
    Temporal change of seismic Earth's inner core phases: Inner core differential rotation or temporal change of inner core surface?
    Presented at Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Me, \& \LWen\ (2017).
    Seismological evidence for a localized mushy zone at the Earth's inner core boundary.
    Presented at 2017 Annual Meeting of Chinese Geoscience Union, Beijing, China.
\item
    \Me, \& \LWen\ (2016).
    Seismic structures of the Earth's inner core boundary beneath the Bearing sea and Mexico.
    Abstract DI43A-2657 presented at 2016 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Me, \& \LWen\ (2015).
    Varying seismic property of the Earth's inner core boundary.
    Abstract DI33A-2606 presented at 2015 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Me, \& \LWen\ (2014).
    Seismic study on the properties of the Earth's inner core boundary.
    Abstract DI31B-4269 presented at 2014 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Me, \& \LWen (2014).
    Topography and properties of the Earth's inner core boundary。
    Abstract presented at 2014 Annual Meeting of Chinese Geophysical Society, Beijing, China.,
\item
    \XChen, \Me, \& \LWen\ (2013).
    Seismic tracking of hurricane sandy.
    Abstract S11A-2296 presented at 2013 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Me, \& \LWen\ (2013).
    Regional topography variation of Earth's inner core boundary.
    Abstract DI23A-2282 presented at 2013 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \MZhang, \Me, \& \LWen\ (2013).
    A new method for earthquake determination: stacking multiple-station autocorrelograms.
    Abstract S51A-2301 presented at 2013 AGU Fall Meeting, San Francisco, CA, USA.
\item
    \Me, \& \LWen\ (2013).
    Simulating wave propagation in a faulted medium using a finite difference method.
    Abstract presented at 2013 Annual Meeting of Chinese Geophysical Society, Kunming, Yunnan, China.
\item
    \Me, \& \LWen\ (2012).
    Simulating wave propagation in a faulted medium using a 3D finite difference method.
    Abstract S43A-2458 presented at 2012 AGU Fall Meeting, San Francisco, CA, USA.
\end{etaremune}
