\section{会议摘要}

\subsection{口头报告}

\begin{etaremune}
\item
	\Me\ (2022).
	Source spectra and stress drops of small-to-moderate earthquakes beneath Tonga and the Alaska Peninsula.
	2022/2021 Annual Meeting of Chinese Geosciecen Union, online.
\item
	\Me, \& \SWei\ (2021).
    Source spectra and stress drops of small-to-moderate earthquakes beneath the Alaska peninsula.
    2021 AGU Fall Meeting, online. ID: T54A-11.
\item
    \Me, \& \LWen\ (2017).
    Seismological evidence for a localized mushy zone at the Earth's inner core boundary.
    2017 Annual Meeting of Chinese Geoscience Union, Beijing, China.
\end{etaremune}

\subsection{张贴海报}

\begin{etaremune}
\item
	\YZhang, Byrnes, J. S., \SWei, \Me, \FWang, \& Bezada M. (2021).
    P-wave attenuation tomography of the Tonga-Lau mantle wedge improved
    by a Bayesian Monte Carlo approach and independently constrained source spectra.
    2021 AGU Fall Meeting, online. ID: S25D-0276.
\item
	Meghan, J., Grund, M., Schlitzer, W., Leong, W. J., \Me, \JYao, \& \LUieda\ (2021).
    PyGMT: An open-source Python library for geospatial processing, analysis, and visualization.
    2021 AGU Fall Meeting, online. ID: IN55C-08.
\item
	\SWei, \YZhang, \Me, \& \DWiens\ (2021).
    New advances in body-wave attenuation studies of the Tonga subduction zone.
    2021 AGU Fall Meeting, online. ID: S23B-05.
\item
	\SWei, \PShearer, \CLithgowBertelloni, \LStixrude, \& \Me\ (2021).
    Oceanic plateau of the Hawaiian mantle plume head subducted to the uppermost lower mantle.
    EGU General Assembly 2021, online. ID: EGU21-13874.
\item
	\Me, \WWang, \FWang, \& \SWei\ (2020).
    Source spectra of intermediate-depth and deep earthquakes in the Tonga subduction zone.
    2020 AGU Fall Meeting, online. ID: S054-0012.
\item
	\SWei, \Me, \PShearer, \MLv, \SDorfman, \CLithgowBertelloni, \& \LStixrude\ (2020).
    Compositional heterogeneities in the mid-mantle revealed by seismic discontinuities and reflectors.
    2020 AGU Fall Meeting, online. ID: DI016-0008.
\item
	\Me, \WWang, \& \SWei\ (2019).
    Source spectra and stress drop of deep earthquakes in the Tonga subduction zone.
    2019 AGU Fall Meeting, San Francisco, CA, USA. ID: S13C-0458.
\item
    \Me, \SWei, \& \PShearer\ (2019).
    Global variations of the 520-km discontinuity.
    Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Me, \SWei, \& \PShearer\ (2018).
    Global variations of the 520-km discontinuity.
    2018 AGU Fall Meeting, Washington, DC, USA. ID: DI31C-0024.
\item
    \Me, \JYao, \& \LWen\ (2017).
    Collapse and earthquake swarm after North Korea's 3 September 2017 nuclear test.
	2017 AGU Fall Meeting, New Orleans, LA, USA. ID: S43H-2968.
\item
    \Me, \& \LWen\ (2017).
    Three types of Earth's inner core boundary.
    2017 AGU Fall Meeting, New Orleans, LA, USA. ID: DI33B-0404.
\item
    \JYao, \Me, \& \LWen\ (2017).
    High-precision location, yield and tectonic release of North Korea's 3 September 2017 nuclear test.
    2017 AGU Fall Meeting, New Orleans, LA, USA. ID: S43H-2967.
\item
    \JYao, \Me, \LSun, \& \LWen\ (2017).
    Temporal change of seismic Earth's inner core phases: Inner core differential rotation or temporal change of inner core surface?
    2017 AGU Fall Meeting, New Orleans, LA, USA. ID: DI33B-0405.
\item
    \Me, \& \LWen\ (2017).
    Seismological evidence for a localized mushy zone at the Earth's inner core boundary.
    Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \JYao, \Me, \LSun, \& \LWen\ (2017).
    Temporal change of seismic Earth's inner core phases: Inner core differential rotation or temporal change of inner core surface?
    Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Me, \& \LWen\ (2016).
    Seismic structures of the Earth's inner core boundary beneath the Bearing sea and Mexico.
    2016 AGU Fall Meeting, San Francisco, CA, USA. ID: DI43A-2657.
\item
    \Me, \& \LWen\ (2015).
    Varying seismic property of the Earth's inner core boundary.
    2015 AGU Fall Meeting, San Francisco, CA, USA. ID: DI33A-2606.
\item
    \Me, \& \LWen\ (2014).
    Seismic study on the properties of the Earth's inner core boundary.
    2014 AGU Fall Meeting, San Francisco, CA, USA. ID: DI31B-4269.
\item
    \Me, \& \LWen (2014).
    Topography and properties of the Earth's inner core boundary.
    2014 Annual Meeting of Chinese Geophysical Society, Beijing, China.
\item
    \XChen, \Me, \& \LWen\ (2013).
    Seismic tracking of Hurricane Sandy.
    2013 AGU Fall Meeting, San Francisco, CA, USA. ID: S11A-2296.
\item
    \Me, \& \LWen\ (2013).
    Regional topography variation of Earth's inner core boundary.
    2013 AGU Fall Meeting, San Francisco, CA, USA. ID: DI23A-2282.
\item
    \MZhang, \Me, \& \LWen\ (2013).
    A new method for earthquake determination: stacking multiple-station autocorrelograms.
    2013 AGU Fall Meeting, San Francisco, CA, USA. ID: S51A-2301.
\item
    \Me, \& \LWen\ (2013).
    Simulating wave propagation in a faulted medium using a finite difference method.
    2013 Annual Meeting of Chinese Geophysical Society, Kunming, Yunnan, China.
\item
    \Me, \& \LWen\ (2012).
    Simulating wave propagation in a faulted medium using a 3D finite difference method.
    2012 AGU Fall Meeting, San Francisco, CA, USA. ID: S43A-2458.
\end{etaremune}
